%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Java Software Engineer } % Job title
{Millennium Bank S.A.} % Organization
{Wroclaw, POL} % Location
{Oct. 2019 - PRESENT} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {creating architecture and implementing PSD2 services for Accounts and Payments - Kubernetes, Spring Boot, Kafka, Redis, SqlServer}
		\item {migration IT Systems - Kubernetes, Spring Boot, Oracle}
	\end{cvitems}
}


%---------------------------------------------------------
  \cventry
    {Software Designer \& Developer \/ Team Leader} % Job title
    {Euro Bank S.A.} % Organization
    {Wroclaw, POL} % Location
    {Apr. 2016 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {managing a team of several developers and solution architects}
        \item {development of an architecture for new solutions, migrate monolith system to microservices - Kubernetes, Spring Boot, Oracle, RabbitMQ}
      \end{cvitems}
    }
%--------------------------------------------------------
  \cventry
    {Senior Software Designer \& Developer} % Job title
    {Euro Bank S.A.} % Organization
    {Wroclaw, POL} % Location
    {Jul. 2013 - Mar. 2016} % Date(s)
    {
	 	\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {implementing rest api for mobile banking, new RWD for online.eurobank.pl, authentication method by sms - Spring MVC, Oracle, JMS, WebLogic }
		    \item {taking care of the module responsible for credit insurances}
		\end{cvitems}
	}


%---------------------------------------------------------
  \cventry
    {Software Designer \& Developer} % Job title
    {Euro Bank S.A.} % Organization
    {Wroclaw, POL} % Location
    {Feb. 2009 - Jun. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {analyzing, designing and implementing banking system modules (loans and credits) - Struts, JSP, Oracle, JMS, WebLogic, EclipseLink }
        \item {integration with external systems including backend banking system, SOAP, XML, JSon}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {FM Group World} % Organization
    {Wroclaw, POL} % Location
    {Feb. 2008 - Sep. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {developing software as part internal requirements of the company, JSF, Hibernate, MySql}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Software Specialis} % Job title
    {BLStream} % Organization
    {Wroclaw, POL; Dunfermline, GB-SCT} % Location
    {Oct. 2006 - Jan. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {crm for Play cellular telecommunications provider, the youngest and fastest growing Polish mobile operator for individual clients and companies - JSF, Spring}
        \item {involvement in the international project for Dunfermline Building Society, Scotland Bank leader of mortgage credit - J2EE, JSP, Oracle}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
